---
title: "Lab-9"
author: "21MIA1127 Dishant Naik"
date: "2024-10-04"
output: html_document
---

## 1. A study is performed to obtain the relationship between the medical expenses and the patient’s age. You are given the data as shown in below Table.
### Age Medical expenses
### 15 100
### 32 150
### 55 370
### 65 1000
### 70 1500
```{r}
Age=c(15,32,55,65,70)
Medical_expenses=c(100,150,370,1000,1500)
```

## 1(a) Calculate the appropriate correlation coefficient between the Age and Medical expenses. Comment on the relationship.
```{r}
a=sum((Age-mean(Age))*(Medical_expenses-mean(Medical_expenses)))
b=(sqrt(sum((Age - mean(Age))^2)) * sqrt(sum((Medical_expenses - mean(Medical_expenses))^2)))
a/b
```
```{r}
cor(Age, Medical_expenses)
```

## 1(b) Obtain the regression equation to predict the medical expenses (y) as a function of Age (x).
```{r}
B_1=sum((Age-mean(Age))*(Medical_expenses-mean(Medical_expenses)))/sum((Age-mean(Age))^2)
B_1
B_0=mean(Medical_expenses)-(B_1*mean(Age))
B_0
paste("Y=",B_0,"+(",B_1,"* X)")
model=lm(Medical_expenses~Age)
summary(model)
```

## 1(c) Predict the expense for a 60 year old patient.
```{r}
Y=B_0+(B_1*60)
Y
```

## 2. Consider the following five training examples
### x= (2,3,4,5,6,7)
### y= (3.5,4,4.2,4.8,5,5.2)
```{r}
x=c(2,3,4,5,6,7)
y=c(3.5,4,4.2,4.8,5,5.2)
```

## Write the R script for the following and give your inference.
## 2(a) Find the best linear fit (Y=aX+b).
```{r}
#Y1=a1+(b1*X)
b1 = sum((x-mean(x))*(y-mean(y)))/sum((x-mean(x))^2)
a1 = mean(y)-(b1*mean(x))
b1
a1
paste("Y=",a1,"+(",b1,"* X)")
model=lm(y~x)
summary(model)
```

## 2(b) Plot the model.
```{r}
plot(x, y, main = "Linear Fit", xlab = "X", ylab = "Y", pch = 19)
abline(a = a1, b = b1, col = "red", lwd = 2)
```

## 2(c) Find the residuals.
```{r}
# Calculate the predicted y values (fitted values)
predicted_y=(b1 * x) + a1
# Calculate residuals
residuals=y - predicted_y
# Output residuals
residuals
```

## 2(d) Evaluate the standard errors associated with a and b.
```{r}
n2=6
rss = sum(residuals^2)
s2 = rss / (n2 - 2)

se_a = sqrt(s2 * n2 / (n2 * sum(x^2) - sum(x)^2))
se_b = sqrt(s2 * sum(x^2) / (n2 * sum(x^2) - sum(x)^2))

se_a
se_b
```

## 2(e) Compute R2 and Adjusted R2 statistic
```{r}
tss = sum((y - mean(y))^2)
r_squared = 1 - rss / tss
adj_r_squared = 1 - (1 - r_squared) * (n2 - 1) / (n2 - 2)

r_squared
adj_r_squared
```

## 3. Draw the correlation plot and apply linear regression analysis on any prominent dataset. State the inferences based on the analysis.
```{r}
d = read.csv("C:/Users/Dishant/Downloads/temp.csv")

plot(d$Temperature, d$Humidity, main = "Correlation Plot", xlab = "Temperature", ylab = "Humidity", pch = 19)

# Linear regression
model <- lm(d$Humidity ~ d$Temperature)
abline(model, col = "blue")
```

